Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-04 doc/manuscript/ESSDmanuscript.Rmd
add some content
(transferring over from notes)

Introduction text goes here.
You can change the name of the section if neccessary using `\introduction[modified heading]`.

@@

# Content section one

## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Subsubsection text here.

>>>>

@@

*(Importance of forests for climate change mitigation)*

*(Need for good data in international carbon accounting)*

*(Introduce EFDb & forc)*

Here, we:
(1) clarify C cycle terminology
(2) describe mapping of ForC to IPCC's EFDB,
(3) describe updates to ForC  (ForC v4.0)
(4) summarize the data in ForC that's relevant to EFDB, identifying gaps
(5) provide recommendations for improving data collection, analysis, database, and accounting

# Defining carbon stocks and incremenets

For quantifying forest role in global C cycle, we ultimately care about:
(1) C stocks --stores of C that would be released to the atmosphere upon and use change
(2) C increments -- changes in those C stocks.

## Carbon stocks

Forest ecosystem C stocks may be parsed into pools in various ways. 
IPCC parses into biomass (aboveground and belowground), dead organic matter (dead wood and litter), and soil organic matter (Table 1).
Quantifying these requires a one-time measurement.

\newpage 
**Table 1: variables with definitions and measurement methods.** Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance). (*Currently adding this as a figure (generated from original draft) because kableExtra doesn't seem to work in this template. Table that we want here is "figures_tables/C_pools.csv"*)

```{r, out.width = "12cm", echo = FALSE, fig.cap = "Table 1"}
knitr::include_graphics("figures_tables/C_pools_fig.png")
```

## Carbon increments

C increments are defined as the change over time, in annual increments, in each C pool.
These may be estimated as the difference between C stocks at two time points, or as the difference between inputs and outputs to the pool (i.e., fluxes).
Quantifying these requires at least two measurements.

Fluxes are the inputs and outputs to each pool.

**Figure: schematic illustrating fluxes in and out of each pool**

### 2021-06-04 doc/manuscript/ESSDmanuscript.tex
add some content
(transferring over from notes)

Introduction text goes here. You can change the name of the section if
neccessary using
\texttt{\textbackslash{}introduction{[}modified\ heading{]}}.

@@

\section{Content section one}

\subsection{Subsection Heading Here}

Subsection text here.

\subsubsection{Subsubsection Heading Here}

Subsubsection text here.

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-3}
\end{figure}

>>>>

@@

\emph{(Importance of forests for climate change mitigation)}

\emph{(Need for good data in international carbon accounting)}

\emph{(Introduce EFDb \& forc)}

Here, we: (1) clarify C cycle terminology (2) describe mapping of ForC
to IPCC's EFDB, (3) describe updates to ForC (ForC v4.0) (4) summarize
the data in ForC that's relevant to EFDB, identifying gaps (5) provide
recommendations for improving data collection, analysis, database, and
accounting

\section{Defining carbon stocks and incremenets}

For quantifying forest role in global C cycle, we ultimately care about:
(1) C stocks --stores of C that would be released to the atmosphere upon
and use change (2) C increments -- changes in those C stocks.

\subsection{Carbon stocks}

Forest ecosystem C stocks may be parsed into pools in various ways. IPCC
parses into biomass (aboveground and belowground), dead organic matter
(dead wood and litter), and soil organic matter (Table 1). Quantifying
these requires a one-time measurement.

\newpage

\textbf{Table 1: variables with definitions and measurement methods.}
Definitions from IPCC Table 1.1. (See Table 1.1 in IPCC guidance).
(\emph{Currently adding this as a figure (generated from original draft)
because kableExtra doesn't seem to work in this template. Table that we
want here is ``figures\_tables/C\_pools.csv''})

\begin{figure}
\includegraphics[width=12cm]{figures_tables/C_pools_fig} \caption{Table 1}\label{fig:unnamed-chunk-1}
\end{figure}

\subsection{Carbon increments}

C increments are defined as the change over time, in annual increments,
in each C pool. These may be estimated as the difference between C
stocks at two time points, or as the difference between inputs and
outputs to the pool (i.e., fluxes). Quantifying these requires at least
two measurements.

Fluxes are the inputs and outputs to each pool.

\textbf{Figure: schematic illustrating fluxes in and out of each pool}

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-4}
\end{figure}
